SST_patterns

### 2020-01-20 SST_patterns.Rmd
speading

# Combined_frequency <- Combined_frequency %>% 
  # mutate(t = parse_date(date, format = "%b_%Y"),
         # distance = factor(distance))

@@

ggplot(data = Combined_frequency, aes(x = t, y = number_of_signals)) +
  geom_line(aes(colour = distance)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  labs(x = NULL) +
  facet_wrap(~site) #+
  # theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

@@

```{r}
cor.test(x = Combined_frequency$distance, Combined_frequency$number_of_signals,
    use = "everything", method = "pearson")

>>>>

Combined_frequency <- Combined_frequency %>%
mutate(t = parse_date(date, format = "%b_%Y"),
distance = factor(distance))

@@

ggplot(data = Combined_frequency, aes(x = t, y = number_of_signals)) +
  geom_line(aes(colour = distance)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  # labs(x = NULL) +
  facet_wrap(~site) #+
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

@@

# chi squared test

combined_freq_spread <- spread(Combined_frequency, distance, number_of_signals)
